---
title: "Project2"
author: "Oliver Benton Javier"
date: "February 14, 2015"
output: html_document
---

# Connect data frame to server

```{r}
food <- data.frame(eval(parse(text=substring(getURL(URLencode('http://129.152.144.84:5001/rest/native/?query="select * from MyCSV"'), httpheader=c(DB='jdbc:oracle:thin:@129.152.144.84:1521:ORCL', USER='C##cs329e_obj66', PASS='orcl_obj66', MODE='native_mode', MODEL='model', returnFor = 'R', returnDimensions = 'False'), verbose = TRUE), 1, 2^31-1))))
```

# Show the subset of the data

```{r}
print(tbl_df(food))
```

# Produce 3 interested data wrangling sets of operations using %>%
# What country produces the most food and least food
food  %>% select(COUNTRY, ITEM, UNIT, AMOUNT)  %>% summarise((min_am == min(AMOUNT)),  ITEM == "Food Supply", UNIT == "Grain Equiv. 1000 MT")

# Find bottom 20% of countries that have low food supply
food %>% filter(ITEM == "Food Supply") %>% select(COUNTRY, ITEM, AMOUNT) %>% mutate(amount_percent = cume_dist(AMOUNT)) %>% filter(amount_percent <= .20) %>% arrange(desc(amount_percent)) %>% tbl_df()

# Find top 20% of countries that have high food supply
food %>% filter(ITEM == "Food Supply") %>% select(COUNTRY, ITEM, AMOUNT) %>% mutate(amount_percent = cume_dist(AMOUNT)) %>% filter(amount_percent >= .80) %>% arrange(desc(amount_percent)) %>% tbl_df()

# Plot bottom 20% 
food %>% filter(ITEM == "Food Supply") %>% select(COUNTRY, ITEM, AMOUNT) %>% mutate(amount_percent = cume_dist(AMOUNT)) %>% filter(amount_percent <= .20) %>% arrange(desc(amount_percent)) %>% ggplot(aes(x = COUNTRY, y = amount_percent)) + geom_point() 


# Arrange table to show economic data for the USA
# Arrange table to show economic data for another country

# Produce interesting visualizations of wrangled data set
